### 2016-05-31 untitled.tex
snapshot — work in progress section 2

\subsubsection{Segmented Self-Suspending Tasks (aka Deferrable Tasks)}
\label{sec:segmented}

@@

Recall that the scheduling penalty associated with self-suspensions is maximized when a task defers the completion of one job just until the release of the next job. For example, this effect is illustrated in Figure \ref{fig:not-ok-without-period-enforcement}, which shows a case in which the self-suspension of the higher-priority task $\tau_2$  results in a deadline miss of the lower-priority task $\tau_3$. The root cause is increased interference due to the ``back-to-back'' execution effect~\cite{LSS:87,LSST:91,Ra:90,ABRTW:93,SLS:95}, where two jobs of $\tau_2$ execute in close succession (i.e, separated by less than a period) because the second job self-suspended for a (much) shorter duration than the first job. That is, $\tau_3$ misses its deadline because $\tau_2$ resumed ``too soon.''

@@

@@

Figure \ref{fig:ok-with-period-enforcement} illustrates how this definition of eligibility times restores the schedulability of the task set depicted in Figure~\ref{fig:not-ok-without-period-enforcement}. Consider the eligibility times of the second segment of task $\tau_2$.

@@

The examples in Figures \ref{fig:not-ok-without-period-enforcement} and \ref{fig:ok-with-period-enforcement} suggest an intuition for the benefits provided by period enforcement: computation segments of a self-suspending task $\tau_i$ are forced to execute at least $T_i$ time units apart (hence the name), which ensures that it causes no more interference than a regular (non-self-suspending) sporadic task. Next, we revisit the original analysis of this technique.

@@

%
Central to Rajkumar's analysis~\cite{Raj:suspension1991} is a \emph{task set transformation} that splits each deferrable task with multiple segments into a corresponding number of single-segment deferrable tasks.  In the words of Rajkumar~\cite[Section 3]{Raj:suspension1991}:

>>>>

\subsubsection{Segmented Self-Suspending Tasks}
\label{sec:segmented}

@@

XXX

\subsubsection{The Problem: Back-to-Back Execution}

The scheduling penalty associated with self-suspensions is maximized when a task defers the completion of one job just until the release of the next job.  For example, this effect is illustrated in Figure \ref{fig:not-ok-without-period-enforcement}, which shows a case in which the self-suspension of the higher-priority task $\tau_2$  results in a deadline miss of the lower-priority task $\tau_3$.

The root cause is increased interference due to the ``back-to-back'' execution effect~\cite{LSS:87,LSST:91,Ra:90,ABRTW:93,SLS:95}, where two jobs of $\tau_2$ execute in close succession (i.e, separated by less than a period) because the second job self-suspended for a (much) shorter duration than the first job. In the example shown in Figure \ref{fig:not-ok-without-period-enforcement},  $\tau_3$ misses its deadline because of this effect as $\tau_2$ resumed ``too soon.''

@@

\subsubsection{The Period Enforcement Rule}

@@

\subsubsection{Example: Hiding the Effects of Deferred Execution}

Figure \ref{fig:ok-with-period-enforcement} illustrates how the definition of eligibility time in Equation~\ref{eq:ET-def} restores the schedulability of the task set depicted in Figure~\ref{fig:not-ok-without-period-enforcement}. Consider the eligibility times of the second segment of task $\tau_2$.

@@

The examples in Figures \ref{fig:not-ok-without-period-enforcement} and \ref{fig:ok-with-period-enforcement} suggest an intuition for the benefits provided by period enforcement: computation segments of a self-suspending task $\tau_i$ are forced to execute at least $T_i$ time units apart (hence the name), which ensures that it causes no more interference than a regular (non-self-suspending) sporadic task.

\subsection{Incompatibility with the Dynamic Self-Suspension Model}

 Next, we revisit the original analysis of this technique.

@@

Central to Rajkumar's analysis~\cite{Raj:suspension1991} is a \emph{task set transformation} that splits each deferrable task with multiple segments into a corresponding number of single-segment deferrable tasks.  In the words of Rajkumar~\cite[Section 3]{Raj:suspension1991}:
